---
title: "Abstract Writing"
#subtitle: "Short descriptions that inform and persuade"  
author: "Alex Norman & Jack Tsonis"
institute: "Western Sydney University"
date: "*November 25, 2019*"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["assets/xaringan-themer.css", "xaringan-themer.css"]
    seal: true # show a slide with YAML info
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      #ratio: "16:9"
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE}
library(xaringanthemer)
solarized_light(
  #primary_color = "#1F4257", 
  #secondary_color = "#F97B64",
  #base_color = "#1c5253",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Droid Mono")
)

#library(xaringanthemer)
#solarized_dark(
#  code_font_family = "Fira Code",
#  code_font_url    = "https://cdn.rawgit.com/tonsky/FiraCode/1.204/distr/fira_code.css"
#)
```


class: center, middle

# Abstract

### /æb.strækt/

.Large[a summary of the contents of a book, article, or speech]

---
class: inverse, center, middle

# Get Started

### What is your research about?

Freewrite 3-4 sentences that explain what you are trying to do.

---
class: 

# Why do abstracts matter?

--

.pull-left[
### For the text

#### To summarise the contents and structure.

* Ideally an abstract will be a condensed version of the text
* Functionally similar to a contents page
* Title and abstract work together for search engine purposes
]

--

.pull-right[
### For the reader

#### To **inform** and **persuade** them to read on
* This helps readers determine if they ought to read the article (persuasion by subject matter)
* This helps the reader to understand *why* they ought to read it (persuasion by value)
]

---
class: center, middle

## All your writing should be in the service of your readers

We want to help your readers think better about the world. 

Our labour is in the direction of making readers' jobs easier.

The abstract to your paper/article/book is your first step in helping colleagues.

--

### Your job is to make your text <br>**valuable for** your **colleagues**

---
class: middle, left

# An Abstract for Today's Session

#### Many higher degree research students have to write abstracts for thesis proposals, journal articles, and conference presentations as part of their candidature. While there is a wealth of advice about writing, both in the humanities and the sciences, the steps required to produce a well-written abstract can be difficult to find. This workshop presents information about abstract writing and puts it into a 'function-based' framework that students can use to develop their writing skills. This framework helps students see abstract writing as a step-wise procedure, and helps them to write abstracts that are useful for readers.

---

# The 4-Function Method

1. **Focus**
  * What is the general context? What is the general problem? 
  
2. **Locate**
  * What is the specific research problem? What is the specific context?
  * What is the justification for examining the specific problem?
  
3. **Explain**
  * What are you going to do/what did you do about the problem?
  * What should the reader expect to find in the text?
  
4. **Implications**
  * What becomes possible because of this research? Conceptually, theoretically, procedurally? 
  * How does the research contribute to the field?
  * How/why does the text help colleagues specifically?

---
class: left

# Today's Abstract

.left-column[
<br>
<br>
**Focus ->**

<br>
<br>
<br>
**Locate ->**

<br>
<br>
<br>
**Explain ->**

<br>
<br>
<br>
**Implicate ->**
]

.right-column[
#### Many higher degree research students have to write abstracts for thesis proposals, journal articles, and conference presentations as part of their candidature. 
####While there is a wealth of advice about writing, both in the humanities and the sciences, the steps required to produce a well-written abstract can be difficult to find.
####This workshop presents information about abstract writing and puts it into a 'function-based' framework that students can use to develop their writing skills.
####This framework helps students see abstract writing as a step-wise procedure, and helps them to write abstracts that are useful for readers.
]

---
class: center, middle

# Thank you!

Presentation slides will be available on my website later today.


**Contact Details**

[`r icon::fa("paper-plane")` a.norman@westernsydney.edu.au](mailto:a.norman@westernsydney.edu.au)

[`r icon::fa("link")` www.dralexnorman.net](https://www.dralexnorman.net)

[`r icon::fa("twitter")` @Aarleks](https://twitter.com/Aarleks)

[`r icon::fa("github")` @Aarleks](https://github.com/Aarleks)

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).

